\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}


\minutesstyle{
columns = {1},
header =  {list}, %or {table},
vote = {list}, %or {table},
contents = {true}, %or {false}
}

\title{Collection of minutes}
\author{\LaTeXe}

\begin{document}

\begin{Minutes}{babyMIND software meeting}
%%\subtitle{}
%%\moderation{}
\minutetaker{Sven-Patrik Hallsj\"o}

\participant{Saba Parsa, Ryan Bayes, Etam Messomo, Alexander Izmaylov}
%\missing[with excuse]{no excuse}
%%\missingExcused{}
%%\missingNoExcuse{}
%\guest{}
\minutesdate{May 27, 2016}
%%\starttime{}
%%\endtime{}
\location{Skype}
%%\cc{}
\maketitle

\topic{Clashing T2K meeting}
Alexander Izmaylov informs us that there is a T2K collaboration meeting that clashes with this meeting.

\topic{Current progress}
Etam Messomo informs from Wednesday, trigger system and assembly zone almost complete.
All modules for beam test moved to assembly zone. 
Scintillating slabs, have been compared.
Hardware, working to get out timing information and amplitude in the same data stream.

Ryan Bayes informs of the work in Glasgow, Sven-Patrik Hallsj\"o has worked with reconstruction, cleaning up bugs, and improved the code and reconstruction efficiency significatly. This will be presented on our Wednesday meeting.
Working now with testbeam digitization and reconstruction.

\topic{T2K code}
Alexander Izmaylov is talking to T2K and will hopefully be able to share the code soon.

\topic{Next meeting}
Friday the 3/6-16 at 10 am BST via Skype.

\end{Minutes}

\end{document}