\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}


\minutesstyle{
columns = {1},
header =  {list}, %or {table},
vote = {list}, %or {table},
contents = {true}, %or {false}
}

\title{Collection of minutes}
\author{\LaTeXe}

\begin{document}

\begin{Minutes}{babyMIND software meeting}
%%\subtitle{}
%%\moderation{}
\minutetaker{Sven-Patrik Hallsj\"o}

\participant{Saba Parsa, Ryan Bayes, Etam Messomo, Tatiana Ovsiannikova}
%Alexander Izmaylov
%\missing[with excuse]{no excuse}
%%\missingExcused{}
%%\missingNoExcuse{}
%\guest{}
\minutesdate{June 3, 2016}
%%\starttime{}
%%\endtime{}
\location{Skype}
%%\cc{}
\maketitle

\topic{DAQ}
- DAQ
Ryan Bayes asked: "What is the format of calibration data?" Glasgow suggests using an XML file or text file.
Etam Messomo replied, xml for front end board, atleast for the configuration.

Etam Messomo adds some construction data:
\begin{itemize}
\item Pitch 10.25mm for bars
\item No gaps between modules.
\item Width 16mm
\item 2 bars 15mm and aluminium.
\item Limited on cable lengths, can not predetermine position of cables on the front-end board. 
\item Module 96 cm x 96 cm.
\end{itemize}

\topic{Test beam simulations}
Sven-Patrik Hallsj\"o mentioned that simulation works, only issue now is clustering algorithms. We need to implement plane number for hit from a map containing barnumber, position and plane.

Saba Parsa replies that she will provide proper maps.

\topic{Next meeting}
Friday the 10/6-16 at 10 am BST via Skype.

\end{Minutes}

\end{document}